\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-10-06 Latex/paper.tex
#cms convexity

\begin{align}
CA_{CMS}(T_a,T_b) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
&\approx  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right)
\end{align}

>>>>

\begin{align}
CA_{CMS}(T_a,T_b) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
&\approx  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
& \approx \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
\end{align}
